---
title: "MARBLE2022 Work"
author: "Aaron Micah Green"
date: "3/8/2022"
output: pdf_document
---

```{r setup, include=FALSE}
# Set the default CRAN repository
local({r <- getOption("repos")
       r["CRAN"] <- "http://cran.r-project.org" 
       options(repos=r)
})

# Set code chunk defaults
knitr::opts_chunk$set(echo = TRUE)

# Load required packages; install if necessary
# CAUTION: DO NOT interrupt R as it installs packages!!
if (!require("ggplot2")) {
  install.packages("ggplot2")
  library(ggplot2)
}

if (!require("knitr")) {
  install.packages("knitr")
  library(knitr)
}

if (!require("dplyr")) {
  install.packages("dplyr")
  library(dp)
}

if (!require("RColorBrewer")) {
  install.packages("RColorBrewer")
  library(RColorBrewer)
}
if (!require("beeswarm")) {
  install.packages("beeswarm")
  library(beeswarm)
}
if (!require("tidyverse")) {
  install.packages("tidyverse")
  library(tidyverse)
}
if (!require("ggbeeswarm")) {
  install.packages("ggbeeswarm")
  library(ggbeeswarm)
}
if (!require("xts")) {
  install.packages("xts")
  library(xts)
}
if (!require("plotly")) {
  install.packages("plotly")
  library(plotly)
}
if(!require("lubridate")) {
  install.packages("lubridate")
  library(lubridate)
}
if(!require("survival")) {
  install.packages("survival")
  library(survival)
}
if(!require("survminer")) {
  install.packages('survminer')
  library(survminer)
}
if(!require("ranger")){
  install.packages("ranger")
  library(ranger)
}
if(!require("ggfortify")){
  install.packages("ggfortify")
  library(ggfortify)
}

source("loadData.r")
```
# Convert Data to Appropriate Format for Survival Analysis
  For tracking loans we can filter out all but a few features of the data:
  
```{r}
timeFinal <- max(df$timestamp)

# Build a table of transaction summary statistics:
transactionSummaries <- df %>%
  group_by(type) %>%
  summarise(count = n(), meanValue = mean(amountUSD), medianValue = median(amountUSD), meanPrinciaplAmount = mean(amountUSDPrincipal), meanCollateralAmount = mean(amountUSDCollateral))

coinSummaries <- df %>%
  group_by(reserve, type) %>%
  summarise(count = n(), totalValue = sum(amountUSD), stableCoin) %>%
  distinct()
```

## Any-To-Any Setup:
```{r}
anyToAny <- df %>%
  group_by(user) %>%
  arrange(timestamp) %>%
  mutate(nextTransactionTimestamp = lead(timestamp), nextTransactionType = lead(type), nextTransactionReserve = lead(reserve)) %>%
  mutate(timeDiff = case_when(!is.na(nextTransactionTimestamp) ~ nextTransactionTimestamp - timestamp,
         TRUE ~ timestamp - timeFinal)) %>%
  mutate(status = case_when(timeDiff < 0 ~ 0, timeDiff >= 0 ~ 1)) %>%
  mutate(timeDiff = abs(timeDiff)) %>%
  select(user, reserve, type, timeDiff, status, nextTransactionType, nextTransactionReserve) %>%
  ungroup()

anyToAnyFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ type, data = anyToAny)

anyToAnyPlot <- ggsurvplot(anyToAnyFit, censor = FALSE)

anyToAnyPlot

anyToAny <- anyToAny %>%
  mutate(nextTransactionBorrow = (nextTransactionType == "borrow")) %>%
  mutate(nextTransactionCollateral = (nextTransactionType == "collateral")) %>%
  mutate(nextTransactionDeposit = (nextTransactionType == "deposit")) %>%
  mutate(nextTransactionLiquidation = (nextTransactionType == "liquidation")) %>%
  mutate(nextTransactionRedeem = (nextTransactionType == "redeem")) %>%
  mutate(nextTransactionRepay = (nextTransactionType == "repay")) %>%
  mutate(nextTransactionSwap = (nextTransactionType == "swap")) 

```

## Deposit-to-Any Analysis:
```{r}
depositToAny <- anyToAny %>%
  filter(type == "deposit")

numTypesAfterDeposit <- depositToAny %>%
  group_by(nextTransactionType) %>%
  summarise(count = n()) %>%
  mutate(percentage = count*100 / length(deposits$timestamp))

kable(numTypesAfterDeposit)
  

depositToAnyFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ nextTransactionType, data=depositToAny)

depositToAnyPlot <- ggsurvplot(depositToAnyFit, xlab = "Time (days)", ylab = "Probability of No Subsequent Transactions", censor = FALSE, legend = c(0.8,0.6), legend.title = "Next Transaction Type (Percentage)", legend.labs = c("Borrow (10.74%)", "Collateral (32.62%)", "Deposit (27.11%)", "Liquidation (0.22%)", "Redeem (25.69%)", "Repay (2.68%)", "Swap (0.13%)"), xlim = c(0,50), break.time.by = 5, conf.int = TRUE, pval = TRUE, pval.coord = c(10, 0.5))

depositToAnyPlot
```
```{r}
depositToAnyFitHours <- survfit(Surv(as.numeric(timeDiff/3600), as.numeric(status)) ~ nextTransactionType, data=depositToAny)

depositToAnyMedians <- surv_median(depositToAnyFitHours)

kable(depositToAnyMedians)

median(depositToAny$timeDiff) / 3600

depositToAnyCox <- coxph(Surv(as.numeric(timeDiff/3600), as.numeric(status)) ~ nextTransactionBorrow + nextTransactionCollateral + nextTransactionDeposit + nextTransactionLiquidation + nextTransactionRedeem + nextTransactionRepay + nextTransactionSwap, data = depositToAny)
summary(depositToAnyCox)
```


## Borrow to Any Analysis:
```{r}
borrowToAny <- anyToAny %>%
  filter(type == "borrow")

borrowToAnyFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ nextTransactionType, data=borrowToAny)

borrowToAnyPlot <- ggsurvplot(borrowToAnyFit, xlab = "Time (days)", ylab = "Probability of No Subsequent Transactions", title = "How Quickly Do Users Act After Borrowing Funds?", censor = FALSE, legend = c(0.8,0.6), legend.title = "Next Transaction Type", legend.labs = c("Borrow", "Collateral", "Deposit", "Liquidation", "Redeem", "Repay", "Swap"), xlim = c(0,50), break.time.by = 5)

borrowToAnyPlot
```
## Borrow to Repay Analysis:
```{r}
borrows <- borrows %>%
  mutate(ID = row_number())

borrowsToRepays <- left_join(borrows, repays, by = c("user", "reserve")) %>%
  rename(borrowTime = timestamp.x) %>%
  rename(repayTime = timestamp.y) %>%
  group_by(ID) %>%
  mutate(status = case_when(borrowTime >= max(repayTime) ~ 0,
                            is.na(repayTime) ~ 0,
                            TRUE ~ 1)) %>%
  distinct()
         
censoredBorrows <- borrowsToRepays %>%
  filter(status == 0) %>%
  group_by(ID) %>%
  summarise(ID, user, timeDiff = timeFinal - borrowTime, status, reserve) %>%
  distinct()
  
uncensoredBorrows <- borrowsToRepays %>%
  filter(status == 1) %>%
  filter(repayTime > borrowTime) %>%
  summarise(ID, user, timeDiff = min(repayTime) - borrowTime, status, reserve) %>%
  distinct()

allBorrowsToRepays <- bind_rows(censoredBorrows, uncensoredBorrows) %>%
  arrange(ID)
  

borrowToRepayFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ 1, data=allBorrowsToRepays)

borrowToRepayPlot <- ggsurvplot(borrowToRepayFit, xlab = "Time (days)", ylab = "Probability of No Repayments", title="How Long Do Users Wait to Repay Loans?", legend = "none", censor=FALSE)

borrowToRepayPlot

```

```{r}
borrowsToRepaysStable <- allBorrowsToRepays %>%
  left_join(reserveTypes) %>%
  filter(reserveType == "Stable")

borrowsToRepaysStableFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ reserve, data=borrowsToRepaysStable)

borrowsToRepaysStablePlot <- ggsurvplot(borrowsToRepaysStableFit, xlab="Time (days)", ylab="Probability of No Repays", title="How Long Do Users Wait to Repay Stable Coins?", legend.title="", censor=FALSE, conf.int = FALSE)

borrowsToRepaysStablePlot
```

```{r}
borrowsToRepaysNonStable <- allBorrowsToRepays %>%
  left_join(reserveTypes) %>%
  filter(reserveType == "Non-Stable")

borrowsToRepaysNonStableFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ reserve, data=borrowsToRepaysNonStable)

borrowsToRepaysNonStablePlot <- ggsurvplot(borrowsToRepaysNonStableFit, xlab="Time (days)", ylab="Probability of No Repays", title="How Long Do Users Wait to Repay Non-Stable Coins?", legend.title="", censor=FALSE, conf.int = FALSE)

borrowsToRepaysNonStablePlot
```

```{r}
borrowsToRepaysSplit <- allBorrowsToRepays %>%
  left_join(reserveTypes)

borrowsToRepaysSplitFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ reserveType, data=borrowsToRepaysSplit)

borrowsToRepaysSplitPlot <- ggsurvplot(borrowsToRepaysSplitFit, xlab="Time (days)", ylab="Probability of No Repays", censor=FALSE, legend.title = "Coin Type", legend.labs = c("Non-Stable (15.40%)", "Stable (84.60%)"), legend = c(0.8, 0.7), pval = TRUE, conf.int = TRUE, xlim = c(0, 10))

borrowsToRepaysSplitPlot
```

```{r}
allBorrowsToRepaysNoNA <- allBorrowsToRepays %>%
  filter(status == 1)
km_fitAllCoins <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status))~reserve, data=allBorrowsToRepaysNoNA)
medianTimeToRepay <- surv_median(km_fitAllCoins)%>%
  mutate(reserve = str_sub(strata, start=9))%>%
  left_join(reserveTypes)

kable(medianTimeToRepay)

densityPlotTimeToRepay <- medianTimeToRepay  %>%
  ggplot(aes(x=median, color=reserveType)) + geom_density() +
  xlab("Time Elapsed Before Loan Repayment (in Days)") +
  ylab("Proportion of Users") + theme_classic() +
  labs(color = "Coin Type") + theme(legend.position = c(0.8, 0.5))

densityPlotTimeToRepay
```

## Borrow To Liquidation Analysis:
```{r}
borrowsToLiquidations <- left_join(borrows, liquidations, by = c("user")) %>%
  rename(borrowTime = timestamp.x) %>%
  rename(liquidationTime = timestamp.y) %>%
  group_by(ID) %>%
  mutate(status = case_when(borrowTime >= max(liquidationTime) ~ 0,
                            is.na(liquidationTime) ~ 0,
                            TRUE ~ 1)) %>%
  distinct()
         
censoredBorrowsToLiquidations <- borrowsToLiquidations %>%
  filter(status == 0) %>%
  group_by(ID) %>%
  summarise(ID, user, timeDiff = timeFinal - borrowTime, status, reserve) %>%
  distinct()
  
uncensoredBorrowsToLiquidations <- borrowsToLiquidations %>%
  filter(status == 1) %>%
  filter(liquidationTime > borrowTime) %>%
  summarise(ID, user, timeDiff = min(liquidationTime) - borrowTime, status, reserve) %>%
  distinct()

allBorrowsToLiquidations <- bind_rows(censoredBorrowsToLiquidations, uncensoredBorrowsToLiquidations) %>%
  arrange(ID)
  

borrowToLiquidationsFit <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ 1, data=allBorrowsToLiquidations)

borrowToLiquidationPlot <- ggsurvplot(borrowToLiquidationsFit, xlab = "Time (days)", ylab = "Probability of No Repayments", title="How Long Do Loans Last Before Being Liquidated?", legend = "none", censor=FALSE)

borrowToLiquidationPlot
```


```{r}
# Here we set up a survival curve representing all borrows. Any borrow that is followed at any time by the user being liquidated counts as a "death". Any borrow after which no liquidation has yet occurred for the same user is considered censored.
borrows <- borrows %>%
  mutate(ID = row_number())
borrowsThatLiquidated <- left_join(borrows, liquidations, by = c("user", "reserve" = "principalReserve")) %>%
  rename(borrowTime = timestamp.x) %>%
  rename(liquidationTime = timestamp.y) %>%
  group_by(user, borrowTime) %>%
  slice_min(liquidationTime) %>%
  ungroup() %>%
  rename(principalReserve = reserve)
  
borrowsToLiquidations <- left_join(borrows, borrowsThatLiquidated, by = "ID") %>%
  mutate(borrowTime = timestamp, borrowedReserve = reserve) %>%
  select(ID, borrowTime, liquidationTime, principalReserve, collateralReserve, borrowedReserve) %>%
  mutate(timeDiff = case_when(!is.na(liquidationTime) ~ liquidationTime - borrowTime,
                              TRUE ~ borrowTime - timeFinal)) %>%
  mutate(status = case_when(timeDiff <= 0 ~ 0, TRUE ~ 1)) %>%
  mutate(timeDiff = abs(timeDiff)) %>%
  distinct()

borrowsToLiquidationTypes <- left_join(borrowsToLiquidations, reserveTypes, by = c("principalReserve" = "reserve")) %>%
  rename('principalType' = 'reserveType')%>%
  left_join(reserveTypes, by = c("collateralReserve" = "reserve")) %>%
  rename(collateralType = reserveType) %>%
  left_join(reserveTypes, by = c("borrowedReserve" = "reserve")) %>%
  rename(borrowType = reserveType)
  
borrowTypePercentages <- borrowsToLiquidationTypes %>%
  group_by(borrowType) %>%
  summarise(count = n(), count*100 / 124899)

borrowTypePercentages

borrowsToLiquidationsFit <- survfit(Surv(timeDiff/86400, status) ~ borrowType, data=borrowsToLiquidationTypes)

borrowsToLiquidationsPlot <- ggsurvplot(borrowsToLiquidationsFit, xlab="Time (days)", ylab="Probability of No Liquidation", legend.title="Coin Type", censor=FALSE, conf.int = TRUE, legend.labs = c("Non-Stable (15.40%)", "Stable (84.60%)"), legend = c(0.8,0.6), pval = TRUE)


borrowsToLiquidationsPlot


```
```{r}
borrowsToLiquidationTypesNoNA <- borrowsToLiquidationTypes %>%
  filter(!is.na(liquidationTime))
borrowsToLiquidationsMediansFit<- survfit(Surv(timeDiff/86400, status) ~ borrowedReserve, data=borrowsToLiquidationTypesNoNA)
medianTimeToLiquidation <- surv_median(borrowsToLiquidationsMediansFit) %>%
  arrange(median) %>%
  mutate(reserve = str_sub(strata, start=17))%>%
  left_join(reserveTypes, by = "reserve")


densityPlotTimeToLiquidation <- medianTimeToLiquidation  %>%
  ggplot(aes(x=median, color=reserveType)) + geom_density() +
  xlab("Time Elapsed Before Loan Liquidation (in Days)") +
  ylab("Proportion of Users") + theme_classic() +
  labs(color = "Coin Type") +
  theme(legend.position = c(0.8,0.5))

densityPlotTimeToLiquidation

```

```{r}
numAggregateLiqPerUser <- aggregateLiquidations %>%
  group_by(user) %>%
  dplyr::summarise(user_alias, numLiquidations = n()) %>%
  distinct()

loanDataTimeToLiquidate <- left_join(borrows,aggregateLiquidations,by=c("user")) %>%
  dplyr::rename(borrowTime=timestamp) %>%
  dplyr::rename(liquidationTime=liquidationStart) %>%
  group_by(user) %>%
  filter(borrowTime <= liquidationTime) %>%
  mutate(timeDiff=case_when(min(liquidationTime)-min(borrowTime)>0 ~ min(liquidationTime)-min(borrowTime), 
                                      TRUE ~ borrowTime - timeFinal)) %>%
  mutate(status=case_when(timeDiff<=0 ~ 0, timeDiff>0 ~ 1)) %>%
  mutate(timeDiff = abs(timeDiff))%>%
  select(user,reserve,principalReserves,collateralReserves,principalTypes,collateralTypes,liquidationType,timeDiff,status) %>%
  distinct()

loanDataTimeToLiquidate <- left_join(loanDataTimeToLiquidate, reserveTypes, by="reserve") %>%
  mutate(liquidationType2 = if_else(!is.na(collateralTypes), paste(reserveType, collateralTypes, sep=":"), "NA"))

loanDataTimeToLiquidate$liquidationType2 <- na_if(loanDataTimeToLiquidate$liquidationType2, "NA")

liquidationCounts <- loanDataTimeToLiquidate %>%
  group_by(liquidationType2) %>%
  dplyr::summarise(liquidationCount = n(), percent = liquidationCount*100 / 6587) %>%
  arrange(-liquidationCount)

liquidationCounts

```

```{r}
loanDataTimeToLiquidate$principalTypes <- as.factor(loanDataTimeToLiquidate$principalTypes)

loanDataTimeToLiquidate$principalTypes <- fct_relevel(loanDataTimeToLiquidate$principalTypes, c("Non-Stable,Stable", "Non-Stable", "Stable"))

loanDataTimeToLiquidate$collateralTypes <- as.factor(loanDataTimeToLiquidate$collateralTypes)

loanDataTimeToLiquidate$collateralTypes <- fct_relevel(loanDataTimeToLiquidate$collateralTypes, c("Non-Stable,Stable", "Non-Stable", "Stable"))

loanDataTimeToLiquidate <- loanDataTimeToLiquidate %>%
  mutate(principalStable = (principalTypes == "Stable" | principalTypes == "Non-Stable,Stable"), principalNonStable = (principalTypes == "Non-Stable" | principalTypes == "Non-Stable,Stable")) %>%
  mutate(collateralStable = (collateralTypes == "Stable" | collateralTypes == "Non-Stable,Stable"), collateralNonStable = (collateralTypes == "Non-Stable" | collateralTypes == "Non-Stable,Stable"))


loanDataTimeToLiquidate <- loanDataTimeToLiquidate %>%
  mutate(timeDiffDays = as.numeric(timeDiff/86400)) %>%
  mutate(timeDiffWeeks = as.numeric(timeDiffDays/7))
km_fitTimeToLiquidate <- survfit(Surv(timeDiffDays, as.numeric(status)) ~ liquidationType2, data=loanDataTimeToLiquidate)

originalCoxFit <- coxph(Surv(timeDiffDays, as.numeric(status)) ~ liquidationType, data = loanDataTimeToLiquidate)
originalCoxFit

loanDataTimeToLiquidate$liquidationType2 <- as.factor(loanDataTimeToLiquidate$liquidationType2)


coxFit <- coxph(Surv(timeDiffDays, as.numeric(status)) ~ liquidationType2, data = loanDataTimeToLiquidate)
coxFit

coxFitWithInteractionTerm <- coxph(Surv(timeDiffDays, as.numeric(status)) ~ principalStable*collateralStable + principalStable*collateralNonStable + principalNonStable*collateralStable + principalNonStable*collateralNonStable, data = loanDataTimeToLiquidate)
coxFitWithInteractionTerm

kmPlotTimeToLiquidate <- ggsurvplot(km_fitTimeToLiquidate, xlab="Time (Days)", ylab="Probability of No Liquidation", legend.title="Principal:Collateral", censor=FALSE, conf.int = TRUE, legend=c(0.8,0.6), legend.labs = c("Non-Stable: Non-Stable (9.43%)", "Non-Stable: Mixed (0.24%)", "Non-Stable: Stable (1.62%)", "Stable: Non-Stable (86.64%)", "Stable: Mixed (0.83%)", "Stable: Stable (1.22%)"), pval = TRUE)

kmPlotTimeToLiquidate
```

## Build features to cluster the users:
```{r}
timeFinal <- max(df$timestamp)
userActiveTime <- df %>%
  group_by(user) %>%
  dplyr::summarise(firstTransactionTimestamp = min(timestamp), finalTimestamp = max(timestamp), daysSinceFirstTransaction = max((timeFinal-min(timestamp))/86400, 1))

userDailyTransactions <- df %>%
  group_by(user) %>%
  mutate(transactionDay = floor_date(as_datetime(timestamp), unit = "day")) %>%
  group_by(user, transactionDay) %>%
  dplyr::summarise(transactionsPerActiveDay = n())

userActiveDays <- userDailyTransactions %>%
  group_by(user) %>%
  dplyr::summarise(activeDays = n())

userBorrowCounts <- borrows %>%
  group_by(user) %>%
  dplyr::summarise(borrowCount = n(), borrowValue = sum(amountUSD))

userDepositCounts <- deposits %>%
  group_by(user) %>%
  dplyr::summarise(depositCount = n(), depositValue = sum(amountUSD))

userRedeemCounts <- redeems %>%
  group_by(user) %>%
  dplyr::summarise(redeemCount = n(), redeemValue = sum(amountUSD))

userRepayCounts <- repays %>%
  group_by(user) %>%
  dplyr::summarise(repayCount = n(), repayValue = sum(amountUSD))

userLiquidatedCounts <- aggregateLiquidations %>%
  group_by(user) %>%
  dplyr::summarise(liquidatedCount = n(), liquidatedValue = sum(totalPrincipalUSD))

userLiquidationCounts <- liquidationsPerformed %>%
  group_by(user) %>%
  dplyr::summarise(liquidationsPerformed = n(), liquidationsPerformedValue = sum(amountUSDCollateral))

userSwapCounts <- swaps %>%
  group_by(user) %>%
  dplyr::summarise(swapCount = n())

userCollateralCounts <- collaterals %>%
  group_by(user) %>%
  dplyr::summarise(collateralCount = n())

userReservesUsed <- df %>%
  filter(type == "deposit" | type == "borrow") %>%
  group_by(user) %>%
  dplyr::summarise(reservesUsed = n_distinct(reserve))

transactionsMadeOnBehalfOf <- df %>%
  filter(user != onBehalfOf & protocolContract == FALSE) %>%
  select(onBehalfOf) %>%
  rename(user = onBehalfOf) %>%
  group_by(user) %>%
  summarise(onBehalfOfCount = n())
  
transactionsPerformedForOther <- df %>%
  filter(user != onBehalfOf & protocolContract == FALSE) %>%
  select(user) %>%
  group_by(user) %>%
  summarise(performedForOtherCount = n())


userTransactionCounts <- df %>%
  select(user, protocolContract) %>%
  distinct() %>%
  full_join(userBorrowCounts, by = "user") %>%
  full_join(userDepositCounts, by = "user") %>%
  full_join(userRedeemCounts, by = "user") %>%
  full_join(userRepayCounts, by = "user") %>%
  full_join(userLiquidatedCounts, by = "user") %>%
  full_join(userLiquidationCounts, by = "user") %>%
  full_join(userSwapCounts, by = "user") %>%
  full_join(userCollateralCounts, by = "user")

userTransactionCounts[is.na(userTransactionCounts)] = 0

userTransactionCounts <- userTransactionCounts %>%
  mutate(totalTransactionCount = borrowCount + depositCount + redeemCount + repayCount + liquidatedCount + liquidationsPerformed + swapCount + collateralCount)

userActiveCollaterals <- collaterals %>%
  group_by(user, reserve) %>%
  slice_max(timestamp) %>%
  filter(toState == TRUE) %>%
  ungroup() %>%
  group_by(user) %>%
  dplyr::summarise(numActiveCollaterals=n())

userClusteringData <- userTransactionCounts %>%
  mutate(percentDepositRedeem = (depositCount + redeemCount) / totalTransactionCount) %>%
  mutate(averageUSDPerTransaction = (depositValue + redeemValue + repayValue + liquidatedValue + liquidationsPerformedValue + borrowValue) / totalTransactionCount) %>%
  mutate(timesLiquidated = liquidatedCount) %>%
  mutate(liquidationsPerformed = liquidationsPerformed) %>%
  left_join(userActiveTime, by="user") %>%
  mutate(averageTransactionsPerDay = totalTransactionCount / daysSinceFirstTransaction) %>%
  left_join(userActiveDays, by="user") %>%
  mutate(percentageDaysActive = activeDays / daysSinceFirstTransaction) %>%
  left_join(userReservesUsed, by = "user") %>%
  left_join(userActiveCollaterals, by="user") %>%
  mutate(percentDeposit = depositCount / totalTransactionCount, percentRedeems = redeemCount / totalTransactionCount, 
         percentBorrow = borrowCount / totalTransactionCount, percentRepay = repayCount / totalTransactionCount,
         percentSwap = swapCount / totalTransactionCount, percentCollateral = collateralCount / totalTransactionCount,
         percentLiquidations = liquidationsPerformed / totalTransactionCount) %>%
  left_join(transactionsOnBehalfOf, by="user") %>%
  left_join(transactionsPerformedForOther, by = "user")
  
userClusteringData[is.na(userClusteringData)] = 0
```

```{r}
library(factoextra)
library(cluster)
library(fclust)
library(ppclust)
library(e1071)

# First, let's select the features we want to use:
clusteringFeatures <- userClusteringData %>%
  filter(protocolContract == FALSE) %>%
  select(percentDepositRedeem, averageUSDPerTransaction, timesLiquidated, liquidationsPerformed, averageTransactionsPerDay, percentageDaysActive, reservesUsed, collateralCount, onBehalfOfCount, performedForOtherCount)

scaledData <- clusteringFeatures %>% mutate_all(scale)

fuzzyCMeans <- cmeans(data.matrix(scaledData), 4, iter.max = 1000, m = 4)

userClusters <- userClusteringData %>%
  filter(protocolContract == FALSE) %>%
  bind_cols(fuzzyCMeans$cluster)%>%
  dplyr::rename(cluster = `...38`) %>%
  select(user, cluster)

```

## Add the user clusters from fuzzyCMeans to the data and see how survival curves change by cluster

```{r}
loanDataTimeToRepayClustered <- loanDataTimeToRepay %>%
  left_join(userClusters, by = "user")

loanCountReserveClustered <- loanDataTimeToRepayClustered %>%
  dplyr::count(reserve) %>%
  arrange(-n)

loanDataClustered <- loanDataTimeToRepayClustered %>%
  left_join(reserveTypes)

km_fitClustered <- survfit(Surv(as.numeric(timeDiff/86400), as.numeric(status)) ~ cluster, data=loanDataClustered)

kmPlotClustered <- ggsurvplot(km_fitClustered, xlab="Time (days)", ylab="Probability of No Repays", title="How Long Do Users Wait to Repay Loans?", legend.title="", censor=FALSE, conf.int = FALSE)

kmPlotClustered
```